---
title: "Congress Tweets"
output: html_document
date: '2022-11-10'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import Packages
```{r}
libs = c('jsonlite', 'tidyjson', 'ggplot2', 'tidyverse','knitr', 'purrr', 'rvest', 'git2r', 'fs', 'tictoc','tidytext','tm')
invisible(lapply(libs, library, character.only = TRUE))
```

# Load Github data into RDS file
```{r}
# # Single day example ----
# # url <- 'https://alexlitel.github.io/congresstweets/data/2022-11-09.json'
# # today_example <- fromJSON(txt=url)
# 
# # Clone Repository ----
# tic()
# temp_import_dir <- path_temp("githubRepo")
# repo_url <- "https://github.com/alexlitel/congresstweets.git"
# clone(url = repo_url, local_path = temp_import_dir)
# toc()
# 
# # Getting the actual files ----
# #get file names as a list
# files_list <- dir_ls(path = path(temp_import_dir, "data"),
#                      glob = "*.json")
# #parse JSON files into R dataframes, bind them all together
# data_files <- map_df(files_list, fromJSON)
# saveRDS(data_files, "data_files.rds")
```

# Load RDS file
```{r}
congress_tweets <- readRDS("data_files.rds")
```


# Clean up data
```{r}
congress_tweets_clean <- congress_tweets %>%
  # head(20)%>%
  mutate(date_time = lubridate::as_datetime(str_sub(str_replace(time, "T", " "), 0, 19)),
         year = lubridate::year(date_time))%>%
  select(id, screen_name, date_time, year, text, source, user_id, link)

#mutate num words per tweet

```

# 1. What’s the Twitter usage for the users (aka members of Congress) between start and end of the dataset?
```{r}
# Start: June 21, 2017
# End: Nov. 9, 2022



```


# 2. What are the top 20 words that are used in their tweets? What do they tell us about the data?
```{r}
#get a dataframe of English stopwords
en_stopwords = data.frame(word = stopwords("en"))

tic()
frequency_dataframe <- congress_tweets_clean%>%
  select(text)%>%
  unnest_tokens(output=word, input=text, token="tweets")%>% 
  anti_join(en_stopwords) %>% #gets rid of stop words
  count(word)%>% 
  arrange(desc(n))
toc()

```

# 3. Who are the power users?
```{r}
congress_tweets_by_user <- congress_tweets_clean %>%
  group_by(screen_name, user_id)%>%
  tally()%>%
  arrange(desc(n))

congress_tweets_by_user_year <- congress_tweets_clean %>%
  group_by(screen_name, user_id, year)%>%
  tally()%>%
  arrange(desc(n))

#mutate avg num words per tweet

```

# 4.  feel free to add in any other interesting takeaways from the data that you think are worth sharing!
```{r}
#who mentions Donald Trump the most in tweets? over what period of time?



```



